Solving the Poisson-equation in one dimension \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-09-13 Project1/article/article.tex
More theory in article

This pattern can be summarized quite elegantly by the following
difference equations.
\begin{equation}
\beta_i=b_i-\frac{c_{i-1}}{\beta_{i-1}}, \quad
\tilde{f}_i=(\beta_i-\tilde{f}_{i-1}a_i)/\beta_i, \quad i \in [2,n], \quad
\end{equation}

\begin{thebibliography}{10}
  \bibitem{thomasalgo}{Thomas, L.H. (1949), \emph{Elliptic
        Problems in Linear Differential Equations over a
        Network}. Watson Sci. Comput. Lab Report, Columbia University,
      New York.}
\end{thebibliography}

>>>>

This pattern can be summarized nicely by the following
difference equations. This computation will from now on be referred to
as the ``forward substitution''. 
\begin{equation}
\beta_i=b_i-\frac{c_{i-1}}{\beta_{i-1}}, \quad
\tilde{f}_i=(\beta_i-\tilde{f}_{i-1}a_i)/\beta_i, \quad i \in [2,n], \quad
\end{equation}

The Gaussian elimination is not fully complete until a ``backward
substitution'' has been performed as well. This ensures that all
eliments in the row reduced matrix are pivot elements.

\begin{equation}
\left[
\begin{array}{cccc|c}
1 & c_1/\beta_1 & 0 & 0 & \tilde{f}_1 \\
0 & 1 & c_2/\beta_2 & 0  & \tilde{f}_2 \\
0 & 0 & 1 & c_3/\beta_3 & \tilde{f}_3 \\
0 & 0 & 0 & 1 & \tilde{f}_4
\end{array}
\right] \sim
\left[
\begin{array}{cccc|c}
1 & c_1/\beta_1 & 0 & 0 & \tilde{f}_1 \\
0 & 1 & c_2/\beta_2 & 0  & \tilde{f}_2 \\
0 & 0 & 1 & 0 & \tilde{f}_3 -\frac{c_3}{\beta_3}\tilde{f}_4 \\
0 & 0 & 0 & 1 & \tilde{f}_4
\end{array}
\right]
\end{equation}

The notation is updated again to $v_3 =\tilde{f}_3 -
\frac{c_3}{\beta_3}\tilde{f}_4$. By continuing this iterative process
all the was to the beginning of the matrix by backward substitution
leaves us with a new recurence relation.
\begin{equation}
v_i=\tilde{f}_i - \frac{c_i}{\beta_i}\tilde{f}_{i+1}, \quad i \in \{n-1,n-2,\dots,1\}
\end{equation}

\subsection{LU Decomposition}

\section{Results}

\section{Discussion}

\section{Conclusion}

\begin{thebibliography}{10}
  \bibitem{thomasalgo}{Thomas, L.H. (1949), \emph{Elliptic
        Problems in Linear Differential Equations over a
        Network}. Watson Sci. Comput. Lab Report, Columbia University,
      New York.}
    \bibitem{morten}{Hjorth-Jensen, M. (2016). \emph{Computational
        Physics - Lecture Notes 2016}. University of Oslo}
\end{thebibliography}
